---
title: "demo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(DCM) #need to think of a better name eventually
```

# Installation

You can install the development version of DCM from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrewthomasjones/DCM")
```

Dataflow is:


1. Read Data 
2. Process data (generate concepts etc) 
3. Combine processed data with a model
4. Fit model
5. Generate Outputs

# Data

## Built in examples

BW and DCE for now, probably better examples to includ with package later

```{r data}
#built in examples
processedBW<-setUp(BWpriorities)

processedDCE<-setUp(DCEpriorities)

```

## Read in data

```{r data2}

filename<-'/Users/uqajon14/Downloads/R Code_RP SP/RP_SP.txt'
processedRP_SP<-setUp(filename, header = FALSE)

```

## Add remove variables
```{r add}

processedRP_SP_12345 <- select_variables(processedRP_SP, c("V1", "V2", "V3", "V4", "V5"))

processedBW_rem <- remove_variables(processedBW, "Accessibility_BW")

```

I made a rough multicolinearity checker (VIF), probably should add correlation to (but just make it easier can do normally anyway)

```{r mc}


choice_model_vif(processedBW)


```

```{r mc2}

choice_model_vif(processedBW_rem)
cor_mat(processedBW_rem)
vif_check(processedBW_rem)

```

## Join datasets

We can also join datasets if necessary.

```{r join}

#simple row join, i know this example doesnt make sense
processedBW_1 <- setUp(BWpriorities[BWpriorities$ID <= 1176,])
processedBW_2 <- setUp(BWpriorities[BWpriorities$ID > 1176,])
processedBW_all <- row_join_choicedatasets(processedBW_1,processedBW_2)

#processedBW <- setUp(BWpriorities)
# for( i in 1:length(processedBW)){
#   print(paste(i, identical(processedBW[[i]], processedBW_all[[i]])))
# }

processedBWDCE <- join_choicedatasets(processedBW, processedDCE)

```

# Models


## Basic

Fixed, random, one-factor 

```{r basic}

m1BWDCE<-model_generator(processedBWDCE, "fixed")

m2BWDCE<-model_generator(processedBWDCE, "random")

m3BWDCE<-model_generator(processedBWDCE, "one-factor")

```

## EMI

```{r emi}
#create template spreadsheet

createEMIWorkbook(processedRP_SP,  "fixed", "~/Desktop")

createEMIWorkbook(processedRP_SP,  "random", "~/Desktop")

createEMIWorkbook(processedRP_SP,  "one-factor", "~/Desktop")


m1RP_SP <- loadEMIWorkbook(processedRP_SP, "~/Desktop/EMI_fixed.xlsx")
m2RP_SP <- loadEMIWorkbook(processedRP_SP, "~/Desktop/EMI_random.xlsx")
m3RP_SP <- loadEMIWorkbook(processedRP_SP, "~/Desktop/EMI_one-factor.xlsx")

```

## Manual

```{r man}

  beta <- matrix(0, nrow=1, ncol=1)
  delta <- matrix(c(0,-1), nrow=1, ncol=2)
  gamma <- matrix(0, nrow=21, ncol=1)
  epsilon <- matrix(c(rep(1,21),rep(0,21)), nrow=21, ncol=2)

  model_matrices  <- list(
    epsilon_model = epsilon,
    delta_model = delta,
    gamma_model = gamma,
    beta_model = beta,
    epsilon_model_initial = matrix(0.1, nrow = 21, ncol = 1),
    delta_model_initial = NA,
    gamma_model_initial = NA,
    beta_model_initial = NA
  )

m1RP_SP_man <- model_generator(processedRP_SP, model_type = "manual", matrix_list = model_matrices)

#runModel(m1RP_SP_man)
#runModel(m1RP_SP)

```

# Model Fitting

```{r fit, cache=TRUE}

#this actually takes a few minutes maybe
BWDCE_f <- runModel(m1BWDCE)

BWDCE_r <- runModel(m2BWDCE)

BWDCE_of <- runModel(m3BWDCE)



RP_SP_f <- runModel(m1RP_SP)

RP_SP_r <- runModel(m2RP_SP)

RP_SP_of <- runModel(m3RP_SP)

```

# Outputs

## Tables

just plain output
```{r res}
RP_SP_f

```

### One model 

```{r summary,results="asis" }
cat(parPrint(BWDCE_f))

x<-cat(parPrint(BWDCE_f))
#cat(parPrint(RP_SP_r))
#cat(parPrint(BWDCE_of))
```

`r x`

#### Group of models

```{r summary2}
summariseModelList(list(BWDCE_f,BWDCE_r,BWDCE_of))

summariseModelList(list(RP_SP_f ,RP_SP_r ,RP_SP_of))

```

## Graphs

graph will eventually be able to be done from model design also. only works for fixed at the moment, more of a concept for now.


```{r graph1}

processedRP_SP_12345 <- select_variables(processedRP_SP, c("V1", "V2", "V3", "V4", "V5"))
m1RPSP<-model_generator(processedRP_SP_12345, "fixed")
m1RPSP_fit1 <- runModel(m1RPSP)
g<-fixed_model_graph(m1RPSP_fit1)

DiagrammeR::render_graph(g)
```

```{r graph2}
BW_f <- model_generator(processedBW_rem, "fixed")
BW_f_1 <- runModel(BW_f)
g<-fixed_model_graph(BW_f_1)
DiagrammeR::render_graph(g)
```

